%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +33 7 65 80 61 63 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Riad Boussoura} \\ \vspace{1pt}
    Paris, France $|$ \small +33 7 65 80 61 63 $|$ \href{mailto:hello@riadboussoura.com}{\underline{hello@riadboussoura.com}} $|$ 
    \href{https://linkedin.com/in/RiadBsr}{\underline{linkedin.com/in/RiadBsr}} $|$
    \href{https://github.com/RiadBsr}{\underline{github.com/RiadBsr}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sorbonne Paris Nord University}{}
      {Master of Artificial Intelligence \& Computer Vision (Excellence Scholarship)}{Sep. 2023 -- Sep. 2025}
    \resumeSubheading
      {University of Science and Technology (USTHB)}{}
      {Master of Computer Vision \& Bachelor of Software Engineering (Top of Class)}{Sep. 2019 -- Jun. 2023}
    \resumeSubheading
      {Samsung Innovation Campus}{}
      {Artificial Intelligence \& Data Science Certification (Selected Top 30 Nationwide)}{Jun. 2021 -- Sep. 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Computer Vision R\&D Engineer}{Mar. 2025 -- Sep. 2025}
      {GoPro}{Paris, France}
      \resumeItemListStart
        \resumeItem{Architected a "Sim-to-Real" deep learning pipeline to solve parallax artifacts in dual-lens 360° image stitching.}
        \resumeItem{Developed a procedural generation engine in \textbf{Blender (Python API)} to render photorealistic synthetic datasets.}
        \resumeItem{Engineered a custom \textbf{PyTorch} model; validated with ML \& Algorithm teams to outperform the production baseline.}
        \resumeItem{Achieved \textbf{$>50\%$ reduction in processing time} over the legacy algorithm while minimizing seam artifacts.}
      \resumeItemListEnd

    \resumeSubheading
      {Lead Founding Engineer \& CTO}{Jan. 2023 -- Nov. 2024}
      {BargMe Startup}{Remote}
      \resumeItemListStart
        \resumeItem{Engineered a \textbf{vision-integrated product recognition pipeline}, processing real-time mobile camera input to trigger algorithmic recommendations.}
        \resumeItem{Developed the recommendation logic that generates cost-optimized alternative shopping lists based on queries.}
        \resumeItem{Managed product lifecycle from research to deployment on Debian VPS, balancing backend latency with mobile constraints.}
    \resumeItemListEnd

    \resumeSubheading
      {Technical Educator \& 3D Specialist}{Jan. 2022 -- Dec. 2023}
      {SkillDino (InspirationTuts)}{Remote}
      \resumeItemListStart
        \resumeItem{Authored tutorials on 3D Computer Vision (Photogrammetry, NeRFs) for an audience of 300,000+ subscribers.}
        \resumeItem{Produced content bridging 3D software (Blender, Unity) and AI (OpenCV), simplifying complex research papers.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{ASYEL: Sign Language Translation} $|$ \emph{Deep Learning, LSTM, Time-Series}}{Apr. 2022}
          \resumeItemListStart
            \resumeItem{Architected a gesture-to-speech translation pipeline using LSTM networks to classify live sign language sequences.}
            \resumeItem{Solved data scarcity by recording a custom dataset, handling motion capture to feature extraction.}
            \resumeItem{Won \textbf{2nd Prize} at the National Innovation Competition (Ministry of Telecommunication).}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Autonomous Safety \& Fall Detection} $|$ \emph{Python, Pose Estimation, Edge AI}}{Nov. 2021}
          \resumeItemListStart
            \resumeItem{Developed an AI safety module for robotic vacuums to detect unattended incidents using Skeleton Tracking.}
            \resumeItem{Designed human-in-the-loop verification: AI waits for an "OK" gesture to cancel alerts, reducing false positives.}
            \resumeItem{Awarded \textbf{1st Prize} at the Google DevFest AI Hackathon and featured on national television.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Real-Time Driver Monitoring (ADAS)} $|$ \emph{Python, MediaPipe 3D, OpenCV}}{Sep. 2021}
          \resumeItemListStart
            \resumeItem{Engineered a drowsiness/distraction detection system using 3D Facial Mesh to track 468 landmarks in real-time.}
            \resumeItem{Implemented geometric analysis of facial vectors to calculate Eye Aspect Ratio (EAR) and yawning frequency.}
            \resumeItem{Selected as "Judges' Favorite" capstone project at Samsung Innovation Campus.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Computer Vision \& 3D}{: OpenCV, MediaPipe, YOLO, Optical Flow, Stereo Vision, Multi-view Geometry, Depth Est.} \\
     \textbf{Deep Learning}{: PyTorch/TensorFlow, CNNs (U-Net, ResNet), Vision Transformers, GANs, LSTMs, Custom Loss Design, Model Optimization} \\
     \textbf{3D Graphics \& Sim}{: Blender (Procedural Generation, Python API, Physics), Unity, Unreal Engine, Ray Tracing} \\
     \textbf{Software Engineering}{: Python (Expert), C++, C, TypeScript/JavaScript, SQL, Git, Docker, Linux, AWS, ONNX} \\
     \textbf{Data Science}{: NumPy, Pandas, Scikit-learn, Matplotlib, Seaborn, Jupyter}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
